A Computational Account of Default Mode Function\\ by Control Theory and Reinforcement Learning

### 2016-10-25 paper/paper.tex
add a majority of references

\section{Introduction}
%
When left unperturbed, the human brain is not at rest.
Rather, the brain continues to metabolize large quantities of
oxygen and glucose energy to maintain
potentially purposeful neuronal computation
in the absence of a focused behavioral goal
\citep{kenet2003spontaneously, fiser2004small}.
This baseline energy demand is subject to surprisingly little modulations
when mentally processing environmental challenges
(Bzdok and Eickhoff, 2016a).
What has early been described as the "stream of consciousness"
in psychology (James, 1890), found its neurobiological manifestation
in the so-called "default mode network" (DMN)
(Shulman et al., 1997). This networked collection of some of the highest regions in
the human association cortex (Mesulam et al., 1998) consistently
increased in neural activity during
unfocused everyday mind wandering (Raichle et al., 2001).
In the beginning of the 21st century, brain imaging was hence the first technology
to allow for the discovery of a unique brain network that subserves
baseline mental activities (Bzdok et al., 2012; Bzdok et al., 2015).

The DMN appeared to be exclusive in task-induced
deactivation during various psychological experiments.
This processing of unknown information categories in the DMN has
been argued to mediate an evolutionarily conserved function for the individual.
This is all the more likely because the DMN contains the two
biggest hotspots of energy consumption in the entire central nervous system.
DMN activity also persists to a substantial degree during
sleep (Horovitz et al., 2008) and under anesthesia (Greicius et al., 2008).
Today, many authors believe that the DMN implements
probabilistic estimation of past, hypothetical, and future events. This
brain network
might have emerged to continuously predict environmental events using
mental imagery as an evolutionary advantage.
%
However, information processing in the DMN has also repeatedly
been shown to directly impact human behavior. Goal-directed task performance
improved with decreased activity in default mode areas (Weissman et al., 2006)
and increased DMN activity was linked to more task-independent,
yet sometimes useful thoughts (Mason et al., 2007; Seli et al., 2016).
%
Understanding of the overarching DMN function is complicated by
simultaneously controlling perception–action cycles and
maintaining baseline contemplations
across time, splace, and content domains
at the interface of the external world and the self.

@@

of glucose energy consumption in humans (Raichle).

@@

(Goldman-Rakic, 1987), generally considered to

@@

including anesthesia (Fiset et al., 1999),
sleep (Maquet, 2000), and forms of coma (Laureys et al., 1999).

@@

as an "inner minds eye" (Cavanna et al., 2006).

@@

awareness that results from damage in the bilateral parietal cortex.

@@

of the amygdala (Bzdok et al., 2013b).

@@

for biological significance assessment
(Adolphs, 2010; Aggleton et al., 1980; Bzdok et al., 2011;
Ghods-Sharifi et al., 2009; LeDoux, 2007).

@@

strategic selection (Pearson et al., 2009), risk assessment (McCoy and Platt, 2005),
and outcome-contingent behavioral modulation (Hayden et al., 2008),

@@

more specifically implicated in approach-avoidance behavior (Vann et al., 2009).

@@

behavioral strategy in a complex food foraging task (Pearson2009).

@@

subjective target utility (McCoy and Platt, 2005) and integration
across individual decision-making instances (Pearson et al., 2009).

@@

over different paragraphs in an fMRI study on auditory narratives (Simony 2016).

@@

in rabbits (Gabriel and Talk, 2001) and humans
(Rudge and Warrington, 1991; Valenstein et al., 1987).

@@

(Burgess, 2008; Epstein, 2008; Valiquette and McNamara, 2007).

@@

The dmPFC subserves predominantly ambiguous amodal processes
across time, space, and content domains in
sensory-independent top-down pathways.
This DMN node has been described as a “mental sketchpad” (Goldman-Rakic, 1996),
potentially implicated in de-novo generation and binding
of meaning representations instructed by stored semantics and memories.
%
The dmPFC may thus enable inference, representation, and assessment
of one's own and other individuals' action and thoughts.
Generally,
patients with neurological lesions in the prefrontal cortex
are known to adapt to novel situations and stimuli with difficulty
(Stuss, D. T. \& Benson, D. F. The Frontal Lobes, Raven, New York, 1986).
Specifically, neural activity in human dmPFC
reflected expectations about other peoples actions and errors thereof
(Suzuki et al., 2012; van Schie et al., 2004).
dmPFC activity indeed explained the proficiency decline
of inferring other peoples' thoughts in the elderly (Moran et al., 2012).
Some dmPFC neurons in macaque monkeys exhibited a preference
for processing others', rather than own, behavior
with fine-grained adjustment of contextual circumstances (Yoshida et al., 2011).
Also the topographically neighboring dorsal anterior cingulate cortex
has been linked to computing values and efforts of
persisting a behavioral plan versus switching the
environmental context in several lesion studies (Rushworth NN 2016).
%
Such highly abstract neural computations necessarily rely on the
generation of probabilistic internal information drawing from
episodic memory retrieval, generative construction processes,
and explicit knowledge of the external world.
%
According to computational neuroimaging experiments,
the dmPFC activity preferentially models stimulus-value associations of
possible actions that are not actually executed,
whereas the vmPFC activity models value in the environment that leads performed actions
{Nicolle, 2012 \#3750}.

The ventromedial prefrontal cortex (vmPFC) subserves
less ambiguous subjective-value-related evaluative processes
reward-informed and risk estimation of self-relevant environmental stimuli.
This DMN node is more closely associated with
orchestrating adapted behavior by bottom-up-driven
processing of “what matters now”,
probably drawing on model-based value representations
\citep{doherty2015structure}.
Quantative lesion findings across 344 human individuals confirmed
a gross impairment in value-based decision making
(Glaescher et al., 2016).
The vmPFC is preferentially connected with limbic and reward-related areas.
The vmPFC has been observed to have monosynaptical connections
with the nucleus accumbens
in axonal tracing studies in monkeys (Haber et al., 1995; Ferry et al., 2000).
The NAc is thought to be linked to reward mechanisms that not
only modulate motivated behavior towards basic survival needs but also
subserve reinforcement learning in humans more broadly
(O'Doherty 2015).
This is consistent with diffusion MRI (dMRI) tractography in humans and monkeys
(Croxson et al., 2005) that
quantified this brain regions to
be substantially more likely connected to the vmPFC than dmPFC in both species.
Two functional connectivity modalities in humans strongly connected
the vmPFC with the nucleus accumbens, hippocampus (HC),
and posteriomedial cortex.
%
The vmPFC is often proposed to be involved in (external) emotional
reactions and own (visceral) arousal.
Real or imaginged bodily states could be mapped in the vmPFC
as a bioregulatory disposition governing cognition
and decision making (Damasio, 1996; Nauta, 1971)
In neuroeconomic studies of human decision making,
the vmPFC consistently reflects an individual’s subjective
valuation (Behrens et al., 2008; Boorman et al., 2009; Knutson et al., 2005; Plassmann et al., 2007)
This may be why performance within and across participants
was related to state encoding in OFC.
Such a \textit{cognitive map} of action space was argued to encode
the current task state even when states are unobservable from sensory input,
which was shown to be critical for behavior.
The GMV of the vmPFC and nucleus accumbens
correlated with indices of social reward attitudes and
value-guided behavior (Lebreton et al., 2009).
Additionally,
independent whole-brain analyses from structural
neuroimaging studies related the gray-matter volume GMV of the vmPFC,
more consistently than any other
brain region, to indices of
social competence and social network complexity,
among the most complicated decision that humans and monkeys take
(Lebreton et al., 2009; Powell et al., 2010; Lewis et al., 2011; Sallet et al., 2011).
%

The HC is well known to be involved in memory and
spatial navigation in animals and humans
(von Bechterew, 1900; Scoville and Milner, 1957; O’Keefe and Dostrovsky, 1971; Maguire et al., 2000).
Its highly recursive anatomical architecture
may be specifically designed to allow reconstructing
entire episodes of experience from memory fragments.
%
While the HC in the medial temporal lobe system
is traditionally believed to allow remembering the past,
there is now increasing evidence for a role
in constructing mental models in general (Schachter/Buckner;
Maguire 2016).
Indeed,
hippocampal damage is
not only associated with an impairment in reexperiencing the past (i.e., amnesia),
but also thinking about one’s own future and
imagining new fictitious experiences more broadly (Hassabis/PNAS).
Mental scenes created by hippocampus-lesioned patients exposed a lack of
spatial integrity, richness in detail, and overall coherence.
%
Single-cell recordings in the animal hippocampus revealed
some constantly active neuronal ensembles whose firing coincided with
distinct locations in space while the animal navigated through its surroundings.
London taxi drivers, individuals with high performance in spatial navigation,
were shown to exhibit increased grey matter volume in the
posterior hippocampus (Maguire et al. 2006b).
But encoding and generative reconstruction in the hippocampus extends
beyond mere spatial knowledge of the environment.
Based on large-scale recordings of hippocampal neuronal populations,
complex spiking patterns can be followed across extended periods including
their modification of input-free self-generated patterns
after environmental events (buszaki2004 theta oscillations).
Specific spiking sequences, that were elicited in experimental task conditions,
have been shown to be reenacted spontaneously during
quiet wakefulness and sleep \citep{hartley2014space}.
Moreover, spike sequences measured in hippocampal place cells of rats
featured reoccurrence directly after experimental trials
as well as directly before upcoming experimental trials (Diba + Buzsaki 2007).
Such hippocampal ensemble burts during rest and sleep
have been proposed to be critical in communicating local information
to the neocortex for long-term storage, potentially also in the nodes of the DMN.
These mechanisms of the hippocampus probably make important contributions to the
recollection of autobiographical memory episodes and other
reexperienced or newly generated mental scenarios (Hassabias2007).
%
The HC thus orchestrates elements of experienced environmental aspects for
consolidations based on reenactment and for integration into
rich mental scene construction. In this view, the HC my even influence
ongoing perception in the current environment (Maguire 2016).
(TODO: relate to self-play in deepmind Go).
(TODO: Kai had an interesting idea: the deja-vu effect
could be when you already accidentally perturbed past
such that it really occures in reality later.)

Finally,
the right and left TPJ are known to have hemispheric differences
according to their cytoarchitectonic borders and gyrification pattern
(Caspers et al., 2008; Caspers et al., 2006).
Neuroscientific investigations on hemispheric functional specialization
have converged to the right versus left cerebral hemisphere as dominant for
attention versus language functions (Broca 1865, Wernicke 1874, Lichtheim 1885;
Gazzaniga, Bogen et al. 1965, Sperry 1982, Stephan, Marshall et al. 2003).
%
The aRTPJ is a key node network is central for
action initiation during externally structured tasks and
sensorimotor control by integrating supramodal stimulus-guided attention
(Corbetta et al., 2002).
Involvement of this DMN node was repeatedly reported in
multi-step action execution \citep{hartmann2005takes},
visuo-proprioceptive conflict (Balslev et al., 2005) and
multi-modal detection of sensory changes across
visual, auditory, or tactile stimulation in a multi-modal fMRI study
(Downar et al., 2000).
In humans, direct electrical stimulation of the
RTPJ during neurosurgery was associated with altered perception
and stimulus awareness (Blanke et al., 2002).
%
Importantly, the RTPJ has been shown to be intimately related to
supramodal prediction and error signaling.
It was argued that the RTPJ encodes actions and ensuing outcomes
without necessarily relating those to outcome value
\citep{liljeholm2013neural, hamilton2008action,
jakobs2009effects}.
Neural activity in the RTPJ has been argued to be responsible
for stimulus-driven attentional reallocation to
salient and surprising sources of information
as a ‘‘circuit breaker’’ that recalibrates control and maintenance systems
(Bzdok et al., 2013; Corbetta et al., 2008).
Indeed, patients with right TPJ damage have particular difficulties
with multistep actions (Hartmann et al. 2005).
In the face of large discrepancies between actual and previously predicted
environmental events the RTPJ acts a potential switch between
externally-oriented mind sets focussed on the
sensory world and internally-oriented mind sets focussed
on self-relevant mind-wandering of possible mental scenarios.
Transient RTPJ in humans for instance disrupted the
impact of predicted intentions of other individuals (Young et al. 2010b),
a capacity believed to be subserved by the DMN.
The RTPJ might hence be an important player that shifts away
from the default active ‘‘internally directed’’ processes
to deal instead with immediate environmental objects and contexts.
(TODO: slow endogeneous changes in state transitions by the policy and value matrices)

The left TPJ in turn exhibits a close topographical relationship to
Wernicke's area
involved in the comprehension or understanding of written and spoken language.
Neurological patients with damage caused to Wernicke's area
have a major impairment of language comprehension
when listening to others or reading a book.
Their speech
preserves natural rhythm and about normal syntax, yet the
voiced sentences are devoid of meaning (i.e., aphasia).
Abstracting from the typical semantic interpretations in linguistics
and neuropsychology,
the LTPJ probably mediates access to and integrating of world knowlege
to model action concepts
\citep{binder2011neurobiology, seghier2013angular}.
For instance, LTPJ lesions also entail problems in recognizing
others' pantomimed action towards objects
without obvious relation to processing any language content
(Varney and Damasio 1987; Rothi et al. 1991; Buxbaum et al. 2005).
%
Also inner speech hinges on knowledge retrieval of statistical structure
about the physical and inter-personal world.
Multivariate volumetric analyses showed that the internal production of
formulated thought ("language of the mind") is closely related to the left TPJ
(Geva et al., 2011).
A number of neuroimaging studies demonstrated LTPJ activity responses
to sementically aberrant words in sentences, which suggests a role
in binding a given semantic concept into an integrated whole.
Further,
episodic memory recall and imagination strongly draw on
complex world knowledge.
Isolated building blocks of world statistics probably get reassembled
in internally generated visual scenarios that
navigate present action, weigh hypothetical possibilities, and forcast the future.
%
The LTPJ may hence facilitate the automated prediction of events
by incorporating experience-derived models of the world
into ongoing action, planning, and problem solving.
% world -> policy matrix driven computation
% self -> value matrix driven computation

>>>>

\section{Introduction}
%
When left unperturbed, the human brain is not at rest.
Rather, the brain continues to metabolize large quantities of
oxygen and glucose energy to maintain
potentially purposeful neuronal computation
in the absence of a focused behavioral goal
\citep{kenet2003spontaneously, fiser2004small}.
This baseline energy demand is subject to surprisingly little modulations
when mentally processing environmental challenges
\citep{raichle2001pnas}.
What has early been described as the "stream of consciousness"
in psychology \citep{james1890principles},
found its neurobiological manifestation
in the so-called "default mode network" (DMN)
\citep{shul1997}. This networked collection of some of the highest regions in
the human association cortex \citep{mesulam1998sensation}
consistently
increased in neural activity during
unfocused everyday mind wandering \citep{raichle2001pnas}.
In the beginning of the 21st century, brain imaging was hence the first technology
to allow for the discovery of a unique brain network that subserves
baseline mental activities
\citep{bzdok2015resting}.

The DMN appeared to be exclusive in task-induced
deactivation during various psychological experiments.
This processing of unknown information categories in the DMN has
been argued to mediate an evolutionarily conserved function for the individual.
This is all the more likely because the DMN contains the two
biggest hotspots of energy consumption in the entire central nervous system.
DMN activity also persists to a substantial degree during
sleep and under anesthesia \citep{randy2008}.
Today, many authors believe that the DMN implements
probabilistic estimation of past, hypothetical, and future events. This
brain network
might have emerged to continuously predict environmental events using
mental imagery as an evolutionary advantage.
%
However, information processing in the DMN has also repeatedly
been shown to directly impact human behavior. Goal-directed task performance
improved with decreased activity in default mode areas \citep{weiss2006}
and increased DMN activity was linked to more task-independent,
yet sometimes useful thoughts
\citep{mason2007, seli2016mind}.
%
Understanding of the overarching DMN function is complicated by
simultaneously controlling perception–action cycles and
maintaining baseline contemplations
across time, splace, and content domains
at the interface of the external world and the self.

@@

of glucose energy consumption in humans \citep{raichle2001pnas}.

@@

\citep{goldman1987development}, generally considered to

@@

including anesthesia,
sleep, and forms of coma \citep{cavanna2006precuneus}.

@@

as an "inner minds eye" \citep{cavanna2006precuneus}.

@@

awareness that results from damage in the bilateral parietal cortex
\citep{balint1909seelenlahmung}.

@@

of the amygdala \citep{bzdok2015subspecialization}.

@@

for biological significance assessment.

@@

strategic selection \citep{pearson2009neurons},
risk assessment \citep{mccoy2005risk},
and outcome-contingent behavioral modulation \citep{hayden2009electrophysiological},

@@

more specifically implicated in approach-avoidance behavior
\citep{vann2009does}.

@@

behavioral strategy in a complex food foraging task \citep{pearson2009neurons}.

@@

subjective target utility \citep{mccoy2005risk} and integration
across individual decision-making instances \citep{pearson2009neurons}.

@@

over different paragraphs in an fMRI study on auditory narratives
\citep{simony2016dynamic}.

@@

in rabbits and humans
\citep{vann2009does}.

@@

\citep{epstein2008parahippocampal, burgess2008spatial, valiquette2007different}.

@@

The dmPFC subserves predominantly ambiguous amodal processes
across time, space, and content domains in
sensory-independent top-down pathways.
This DMN node has been described as a “mental sketchpad”
\citep{goldman1996prefrontal},
potentially implicated in de-novo generation and binding
of meaning representations instructed by stored semantics and memories.
%
The dmPFC may thus enable inference, representation, and assessment
of one's own and other individuals' action and thoughts.
Generally,
patients with neurological lesions in the prefrontal cortex
are known to adapt to novel situations and stimuli with difficulty
\citep{stuss1986frontal}.
Specifically, neural activity in human dmPFC
reflected expectations about other peoples actions and errors thereof.
dmPFC activity indeed explained the proficiency decline
of inferring other peoples' thoughts in the elderly \citep{moran2012social}.
Some dmPFC neurons in macaque monkeys exhibited a preference
for processing others', rather than own, behavior
with fine-grained adjustment of contextual circumstances \citep{yoshida2010neural}.
Also the topographically neighboring dorsal anterior cingulate cortex
has been linked to computing values and efforts of
persisting a behavioral plan versus switching the
environmental context in several lesion studies \citep{kolling2016value}.
%
Such highly abstract neural computations necessarily rely on the
generation of probabilistic internal information drawing from
episodic memory retrieval, generative construction processes,
and explicit knowledge of the external world.
%
According to computational neuroimaging experiments,
the dmPFC activity preferentially models stimulus-value associations of
possible actions that are not actually executed,
whereas the vmPFC activity models value in the environment that leads performed actions
\citep{nicolle2012agent}.

The ventromedial prefrontal cortex (vmPFC) subserves
less ambiguous subjective-value-related evaluative processes
reward-informed and risk estimation of self-relevant environmental stimuli.
This DMN node is more closely associated with
orchestrating adapted behavior by bottom-up-driven
processing of “what matters now”,
probably drawing on model-based value representations
\citep{doherty2015structure}.
Quantative lesion findings across 344 human individuals confirmed
a gross impairment in value-based decision making
\citep{glascher2012lesion}.
The vmPFC is preferentially connected with limbic and reward-related areas.
The vmPFC has been observed to have monosynaptical connections
with the nucleus accumbens
in axonal tracing studies in monkeys \citep{haber1995orbital}.
The NAc is thought to be linked to reward mechanisms that not
only modulate motivated behavior towards basic survival needs but also
subserve reinforcement learning in humans more broadly.
This is consistent with diffusion MRI (dMRI) tractography in humans and monkeys
\citep{croxson2005quantitative} that
quantified this brain regions to
be substantially more likely connected to the vmPFC than dmPFC in both species.
Two functional connectivity modalities in humans strongly connected
the vmPFC with the nucleus accumbens, hippocampus (HC),
and posteriomedial cortex.
%
The vmPFC is often proposed to be involved in (external) emotional
reactions and own (visceral) arousal.
Real or imaginged bodily states could be mapped in the vmPFC
as a bioregulatory disposition governing cognition
and decision making \citep{damasio1996somatic}
In neuroeconomic studies of human decision making,
the vmPFC consistently reflects an individual’s subjective
valuation
\citep{behrens2008associative}.
This may be why performance within and across participants
was related to state encoding in OFC.
Such a \textit{cognitive map} of action space was argued to encode
the current task state even when states are unobservable from sensory input,
which was shown to be critical for behavior.
The GMV of the vmPFC and nucleus accumbens
correlated with indices of social reward attitudes and
value-guided behavior \citep{lebreton2009automatic}.
Additionally,
independent whole-brain analyses from structural
neuroimaging studies related the gray-matter volume GMV of the vmPFC,
more consistently than any other
brain region, to indices of
social competence and social network complexity,
among the most complicated decision that humans and monkeys take
\citep{behrens2009computation}.
%

The HC is well known to be involved in memory and
spatial navigation in animals and humans.
Its highly recursive anatomical architecture
may be specifically designed to allow reconstructing
entire episodes of experience from memory fragments.
%
While the HC in the medial temporal lobe system
is traditionally believed to allow remembering the past,
there is now increasing evidence for a role
in constructing mental models in general
\citep{maguire2016, schacter2007remembering}.
Indeed,
hippocampal damage is
not only associated with an impairment in reexperiencing the past (i.e., amnesia),
but also thinking about one’s own future and
imagining new fictitious experiences more broadly \citep{hassabis2007patients}.
Mental scenes created by hippocampus-lesioned patients exposed a lack of
spatial integrity, richness in detail, and overall coherence.
%
Single-cell recordings in the animal hippocampus revealed
some constantly active neuronal ensembles whose firing coincided with
distinct locations in space while the animal navigated through its surroundings.
London taxi drivers, individuals with high performance in spatial navigation,
were shown to exhibit increased grey matter volume in the
posterior hippocampus \citep{maguire2000navigation}.
But encoding and generative reconstruction in the hippocampus extends
beyond mere spatial knowledge of the environment.
Based on large-scale recordings of hippocampal neuronal populations,
complex spiking patterns can be followed across extended periods including
their modification of input-free self-generated patterns
after environmental events \citep{buzsaki2004large}.
Specific spiking sequences, that were elicited in experimental task conditions,
have been shown to be reenacted spontaneously during
quiet wakefulness and sleep \citep{hartley2014space}.
Moreover, spike sequences measured in hippocampal place cells of rats
featured reoccurrence directly after experimental trials
as well as directly before upcoming experimental trials \citep{diba2007forward}.
Such hippocampal ensemble burts during rest and sleep
have been proposed to be critical in communicating local information
to the neocortex for long-term storage, potentially also in the nodes of the DMN.
These mechanisms of the hippocampus probably make important contributions to the
recollection of autobiographical memory episodes and other
reexperienced or newly generated mental scenarios
\citep{hassabis2007patients}.
%
The HC thus orchestrates elements of experienced environmental aspects for
consolidations based on reenactment and for integration into
rich mental scene construction. In this view, the HC my even influence
ongoing perception in the current environment
\citep{maguire2016}.
% (TODO: relate to self-play in deepmind Go).
% (TODO: Kai had an interesting idea: the deja-vu effect
% could be when you already accidentally perturbed past
% such that it really occures in reality later.)

Finally,
the right and left TPJ are known to have hemispheric differences
according to their cytoarchitectonic borders and gyrification pattern
\citep{seghier2013angular}.
Neuroscientific investigations on hemispheric functional specialization
have converged to the right versus left cerebral hemisphere as dominant for
attention versus language functions.
%
The aRTPJ is a key node network is central for
action initiation during externally structured tasks and
sensorimotor control by integrating supramodal stimulus-guided attention
\citep{corbetta2002control}.
Involvement of this DMN node was repeatedly reported in
multi-step action execution \citep{hartmann2005takes},
visuo-proprioceptive conflict (Balslev et al., 2005) and
multi-modal detection of sensory changes across
visual, auditory, or tactile stimulation in a multi-modal fMRI study
\citep{downar2000multimodal}.
In humans, direct electrical stimulation of the
RTPJ during neurosurgery was associated with altered perception
and stimulus awareness \citep{blanke2002neuropsychology}.
%
Importantly, the RTPJ has been shown to be intimately related to
supramodal prediction and error signaling.
It was argued that the RTPJ encodes actions and ensuing outcomes
without necessarily relating those to outcome value
\citep{liljeholm2013neural, hamilton2008action,
jakobs2009effects}.
Neural activity in the RTPJ has been argued to be responsible
for stimulus-driven attentional reallocation to
salient and surprising sources of information
as a ‘‘circuit breaker’’ that recalibrates control and maintenance systems
\citep{bzdok2013tpj, corbettashul2008}.
% (Bzdok et al., 2013; Corbetta et al., 2008).
Indeed, patients with right TPJ damage have particular difficulties
with multistep actions \citep{hartmann2005takes}.
In the face of large discrepancies between actual and previously predicted
environmental events the RTPJ acts a potential switch between
externally-oriented mind sets focussed on the
sensory world and internally-oriented mind sets focussed
on self-relevant mind-wandering of possible mental scenarios.
Transient RTPJ in humans for instance disrupted the
impact of predicted intentions of other individuals
\citep{young2010disruption},
a capacity believed to be subserved by the DMN.
The RTPJ might hence be an important player that shifts away
from the default active ‘‘internally directed’’ processes
to deal instead with immediate environmental objects and contexts.
% (TODO: slow endogeneous changes in state transitions by the policy and value matrices)

The left TPJ in turn exhibits a close topographical relationship to
Wernicke's area
involved in the comprehension or understanding of written and spoken language.
Neurological patients with damage caused to Wernicke's area
have a major impairment of language comprehension
when listening to others or reading a book.
Their speech
preserves natural rhythm and about normal syntax, yet the
voiced sentences are devoid of meaning (i.e., aphasia).
Abstracting from the typical semantic interpretations in linguistics
and neuropsychology,
the LTPJ probably mediates access to and integrating of world knowlege
to model action concepts
\citep{binder2011neurobiology, seghier2013angular}.
For instance, LTPJ lesions also entail problems in recognizing
others' pantomimed action towards objects
without obvious relation to processing any language content
\citep{varney1987locus}
% (Varney and Damasio 1987; Rothi et al. 1991; Buxbaum et al. 2005).
%
Also inner speech hinges on knowledge retrieval of statistical structure
about the physical and inter-personal world.
Multivariate volumetric analyses showed that the internal production of
formulated thought ("language of the mind") is closely related to the left TPJ
\citep{geva2011neural}.
A number of neuroimaging studies demonstrated LTPJ activity responses
to sementically aberrant words in sentences, which suggests a role
in binding a given semantic concept into an integrated whole.
Further,
episodic memory recall and imagination strongly draw on
complex world knowledge.
Isolated building blocks of world statistics probably get reassembled
in internally generated visual scenarios that
navigate present action, weigh hypothetical possibilities, and forcast the future.
%
The LTPJ may hence facilitate the automated prediction of events
by incorporating experience-derived models of the world
into ongoing action, planning, and problem solving.
% world -> policy matrix driven computation
% self -> value matrix driven computation
